Hypercoercions and a Framework for \\ Equivalence of Cast Calculi

### 2019-12-02 paper.tex
fix typos

Let $v$ range over values. A value is either the unit, a function, a pair, a 
left injection, a right injection, or a casted value. Value typing rules 
restrict the casts in casted values. If the cast is between pre-types, source 
and target types must have the same type constructor at the top ($P_1 \approx 
P_2$). If the cast is from a pre-type to the dynamic type, the pre-type must be 
injectable. The definition of injectable types depends on blame
strategies: for the \lazyD\ strategy, every pre-type is injectable;
for the \lazyUD\ strategy, a pre-types is injectable if all its sub-parts are 
the dynamic type.

@@

We then apply this framework to \lazyD{} hypercoercions
(Section~\ref{sec:hypercoercion-correctness}), where we show that $H$
is an instance of the Lazy D Cast ADT, and therefore
\[
  \evalEqv{\effCEK{H}}{\ineffCEKD}
\]

@@

\begin{definition}[Continuations for the \effCEK{C} machine] 
\label{def:values-effCEK}
  \[
  \begin{array}{lrcl}
  \stxrule{\kappa}{Continuation}{
    \kOOcast{c}{k}
  }
  \stxrule{k}{Pre-continuations}{
    \kOOmt \mid{}
    \kOOconsI{T}{T}{e}{\mathcal{E}}{\kappa} \mid
    \kOOconsII{T}{T}{v}{\kappa} \mid
    \kOOinl{T}{T}{\kappa}
  }
  \stxrulecont{
  	\kOOinr{T}{T}{\kappa} \mid
    \kOOappI{e}{\mathcal{E}}{\kappa} \mid
    \kOOappII{v}{\kappa} \mid
    \kOOcar{\kappa} \mid
    \kOOcdr{\kappa}
  }
  \stxrulecont{
    \kOOcaseI{e}{e}{\mathcal{E}}{\kappa} \mid
    \kOOcaseII{v}{e}{\mathcal{E}}{\kappa} \mid
    \kOOcaseIII{v}{v}{\kappa}
  }
  \end{array}
  \]
\end{definition}

>>>>

Let $v$ range over values. A value is either the unit, a function, a pair, a 
left injection, a right injection, or a casted value. Value typing rules 
restrict the casts in casted values. If the cast is between pre-types, source 
and target types must have the same type constructor at the top ($P_1 \smile 
P_2$). If the cast is from a pre-type to the dynamic type, the pre-type must be 
injectable. The definition of injectable types depends on blame
strategies: for the \lazyD\ strategy, every pre-type is injectable;
for the \lazyUD\ strategy, a pre-types is injectable if all its sub-parts are 
the dynamic type.

@@

We then apply this framework to \lazyD{} hypercoercions $H$
(Section~\ref{sec:hypercoercion-correctness}), where we show that $H$
is an instance of the Lazy D Cast ADT, and therefore
\[
  \evalEqv{\effCEK{H}}{\ineffCEKD}
\]

@@

\begin{definition}[Continuations for the \effCEK{C} machine] 
\label{def:conts-effCEK}
  \[
  \begin{array}{lrcl}
  \stxrule{\kappa}{Continuation}{
    \kOOcast{c}{k}
  }
  \stxrule{k}{Pre-continuations}{
    \kOOmt \mid{}
    \kOOconsI{T}{T}{e}{\mathcal{E}}{\kappa} \mid
    \kOOconsII{T}{T}{v}{\kappa} \mid
    \kOOinl{T}{T}{\kappa}
  }
  \stxrulecont{
  	\kOOinr{T}{T}{\kappa} \mid
    \kOOappI{e}{\mathcal{E}}{\kappa} \mid
    \kOOappII{v}{\kappa} \mid
    \kOOcar{\kappa} \mid
    \kOOcdr{\kappa}
  }
  \stxrulecont{
    \kOOcaseI{e}{e}{\mathcal{E}}{\kappa} \mid
    \kOOcaseII{v}{e}{\mathcal{E}}{\kappa} \mid
    \kOOcaseIII{v}{v}{\kappa}
  }
  \end{array}
  \]
\end{definition}
